---
title: "wrangling data 1.0"
author: "Patrick Burke"
date: "4/4/2022"
output: html_document
---
```{r}
url <- "https://www.mariowiki.com/Mario_Kart_8_Deluxe_in-game_statistics"
mk <- read_html(url)
mk_tab <- mk %>% html_nodes("table")
```

## Kart Scraping

```{r}
karts <- mk_tab[[2]] %>% html_table()

karts <- karts %>%
  row_to_names(row_number = 1)

karts <- karts %>%
  mutate_at(vars(2:14), as.numeric)
```

## Character Scraping

```{r}
chars <- mk_tab[[3]] %>% html_table()

chars <- chars %>%
  row_to_names(row_number = 1) %>%
  slice(1:n()-1)

chars <- chars %>%
  mutate_at(vars(2:14), as.numeric)

chars <- chars %>%
  mutate(Driver = substr(Driver, 1, nchar(Driver)-3))


chars$Driver[14] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[15] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[17] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[18] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[19] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[20] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[21] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[22] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[30] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[31] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[35] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[36] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[38] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[40] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[42] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
chars$Driver[43] = substr(chars$Driver[14], 1, nchar(chars$Driver[14])-3)
```
This is an extremely ineffecient way to make this work. I plan on finding a better way, as I am going to have to do this for the other the dataframes as well.


## Wheel Scraping

```{r}
wheels <- mk_tab[[4]] %>% html_table()

wheels <- wheels %>%
  row_to_names(row_number = 1)

wheels <- wheels %>%
  mutate_at(vars(2:14), as.numeric)
```

## Glider Scraping

```{r}
glider <- mk_tab[[5]] %>% html_table()

glider <- glider %>%
  row_to_names(row_number = 1)

glider <- glider %>%
  mutate_at(vars(2:14), as.numeric)

```

## Big dataset
```{r}
mkfull <- full_join(karts, chars)
mkfull <-full_join(mkfull, glider)
mkfull <- full_join(mkfull, wheels)
```


## One character dataset

```{r}
selected <- mkfull %>%
  filter(Driver == "Koopa Troopa" | Glider == "Parachute" 
         | Tire == "StandardNormal" | Body == "Landship")
```


## This is a dead page. I am most likely done updating this as I have found data which I believe to be tidier. I am keeping this data here in case I need to come back to use this dataset or view the old changes I had made.